Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-03 analysis/paper/paper.Rmd
clarify number of chains run and warmup
Add details of thinning in the models
Remove references to article class (Fundamental/Applied)

Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
These classifications were based on the individual evaluator's judgement of the article.

@@

Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
Each model was run for 4000 iterations in four chains.

@@

The differences between the co-authors' classifications of the article class as `applied` or `fundamental` had no differences in the five articles that were evaluated by all of the co-authors (Figure \@ref(fig:irArtClass)A).
However, there were several differences in evaluators' interpretations of whether or not an article had a molecular focus (Figure \@ref(fig:irArtClass)B).
All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).

@@

# Figures

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}

@@

load(file = here("inst/extdata/m_f1.Rda"))
load(file = here("inst/extdata/m_f2.Rda"))
load(file = here("inst/extdata/m_f3.Rda"))
load(file = here("inst/extdata/m_g1.Rda"))
load(file = here("inst/extdata/m_g2.Rda"))
load(file = here("inst/extdata/m_g3.Rda"))
load(file = here("inst/extdata/m_h1.Rda"))
load(file = here("inst/extdata/m_h2.Rda"))
load(file = here("inst/extdata/m_h3.Rda"))
load(file = here("inst/extdata/m_i1.Rda"))
load(file = here("inst/extdata/m_i2.Rda"))
load(file = here("inst/extdata/m_i3.Rda"))
load(file = here("inst/extdata/m_j1.Rda"))
load(file = here("inst/extdata/m_j2.Rda"))
load(file = here("inst/extdata/m_j3.Rda"))

mod_list <- list(
  pp_check(m_f1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_f2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_f3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_h1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_h2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_h3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_i1),
  pp_check(m_i2),
  pp_check(m_i3)
)

p <- wrap_plots(mod_list, nrow = 4) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A",
                  title = "Bayesian posterior distributions of evaluation score models")

```{r irArtClass, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator classifications of (A) an articles focus being molecular techniques (TRUE/FALSE) and (B) an article's class (Fundamental/Applied). Where all five articles were scored by all five authors to check for agreement between the evaluations.", cache=FALSE, fig.env='figure'}

theme_set(theme_classic())
a <- ggplot(ir, aes(y = doi,
                      fill = molecular)) +
  geom_bar() +
  scale_fill_grey(name = "") +
  ylab("DOI") +
  xlab("Count") +
  ggtitle("Molecular Focus") +
  theme(legend.position = "top")

b <- ggplot(ir, aes(y = doi,
                      fill = art_class)) +
  geom_bar() +
  scale_fill_grey(name = "") +
  xlab("Count") +
  ylab("") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  ggtitle("Article Class") +
  theme(legend.position = "top")

p <- (a | b)
p <- p + plot_annotation(tag_levels = "A",
                         title = "Evaluator agreement in article classifications")

@@

p <- a + b
p <- p + plot_annotation(tag_levels = "A",
                         title = "Evaluator agreement in article reproducibility criteria scoring")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

p <- a + b + c
p <- p +
  plot_annotation(tag_levels = "A")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```

>>>>

@@

Models were fit using the `cumulative(link = "logit")` family function for ordinal scale data.
Each model was run for 6000 iterations in four chains with a warmup of 3000 iterations and thinning set to 1.

@@

All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).

@@

# Figures
\newpage

p <- a + b
p <- p + plot_annotation(tag_levels = "A",
                         title = "Evaluator agreement in article reproducibility criteria scoring") &
  theme(text = element_text("Arial"))

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A, B, C) Publication (Journal Title), (D, E, F) Article Class, (G, H, I) Five Year Impact Factor of Journal, (J, K, L) Journal Open Access Policy, (M, N, O) Year of Publication and (P, Q) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}

@@

load(file = here("inst/extdata/m_f1.Rda"))
load(file = here("inst/extdata/m_f2.Rda"))
load(file = here("inst/extdata/m_f3.Rda"))
load(file = here("inst/extdata/m_g1.Rda"))
load(file = here("inst/extdata/m_g2.Rda"))
load(file = here("inst/extdata/m_g3.Rda"))
load(file = here("inst/extdata/m_h1.Rda"))
load(file = here("inst/extdata/m_h2.Rda"))
load(file = here("inst/extdata/m_h3.Rda"))
load(file = here("inst/extdata/m_i1.Rda"))
load(file = here("inst/extdata/m_i2.Rda"))
load(file = here("inst/extdata/m_i3.Rda"))
load(file = here("inst/extdata/m_j1.Rda"))
load(file = here("inst/extdata/m_j2.Rda"))
load(file = here("inst/extdata/m_j3.Rda"))
load(file = here("inst/extdata/m_k1.Rda"))
load(file = here("inst/extdata/m_k2.Rda"))

mod_list <- list(
  pp_check(m_f1) +
    ggtitle("Code") +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(hjust = 0.5)
    ) +
    ylab("Journal"),
  pp_check(m_f2) +
    ggtitle("Data") +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(hjust = 0.5)
    ),
  pp_check(m_f3) +
    ggtitle("Software") +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      plot.title = element_text(hjust = 0.5)
    ),
  pp_check(m_g1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ) +
    ylab("5 Y IF"),
  pp_check(m_g2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_h1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ) +
    ylab("Year"),
  pp_check(m_h2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_h3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
    ),
  pp_check(m_i1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ) +
    ylab("Access"),
  pp_check(m_i2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_i3) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_j1) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ) +
    ylab("Instructions"),
  pp_check(m_j2) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_j3),
  pp_check(m_k1) +
    ylab("Software"),
  pp_check(m_k2)
)

p <- wrap_plots(mod_list, ncol = 3) +
  plot_layout(guides = "collect") &
  plot_annotation(title = "Bayesian posterior distributions of evaluation score models") &
  theme(text = element_text("Arial"))

@@

@@

p <- a + b + c
p <- p +
  plot_annotation(tag_levels = "A") &
  theme(text = element_text("Arial"))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```
